LAGOS lake depth

### 2020-01-31 figures/01_geometry.Rmd
rm ggplotly tests

# plot of true deepest versus visual centers

gg_scatter_state <- ggplot(data = st_drop_geometry(dt)) + 
  geom_point(aes(x = dist_deepest, y = dist_viscenter, color = state)) +
  geom_abline(aes(intercept = 0, slope = 1)) +
  xlab("Distance to shore from deepest point") +
  ylab("Distance to shore from visual center")

# plotly::ggplotly(gg_test)
# plot(res$dist_deepest, res$dist_viscenter)

>>>>

# plot of true deepest versus visual centers
gg_scatter_state <- ggplot(data = st_drop_geometry(dt)) + 
  geom_point(aes(x = dist_deepest, y = dist_viscenter, color = state)) +
  geom_abline(aes(intercept = 0, slope = 1)) +
  xlab("Distance to shore from deepest point") +
  ylab("Distance to shore from visual center")
